Are environmental and geographic variables effective surrogates for genetic variation in conservation planning?

### 2016-05-06 code/rmarkdown/figures.Rmd
+ figure fixes

@@

@@

# make plot
suppressWarnings(
	ggplot(aes(x=surrogate.held, y=genetic.held), data=curr.DF) +
		theme_classic() +
		theme(strip.background=element_rect(fill='grey20'), strip.text=element_text(color='white', face='italic', size=1)) +
		xlab('Environmental variation secured (%)') +
		ylab('Adaptive genetic variation secured (%)') +
		stat_smooth(method='glm', method.args=list(family='binomial'), fullrange=TRUE,
			se=FALSE, color='blue') +
		geom_point(fill='transparent') +
		geom_text(aes(label=R2_repr), data=curr.DF2, parse=TRUE, hjust=0, size=1, color='blue') +
		facet_wrap(~ Species, ncol=4)
)
```

@@

# make plot
suppressWarnings(
	ggplot(aes(x=surrogate.held, y=genetic.held), data=curr.DF) +
		theme_classic() +
		theme(strip.background=element_rect(fill='grey20'), strip.text=element_text(color='white', face='italic', size=1)) +
		xlab('Geographic variation secured (%)') +
		ylab('Neutral genetic variation secured (%)') +
		stat_smooth(method='glm', method.args=list(family='binomial'), fullrange=TRUE,
			se=FALSE, color='blue') +
		geom_point(fill='transparent') +
		geom_text(aes(label=R2_repr), data=curr.DF2, parse=TRUE, hjust=0, size=1, color='blue') +
		facet_wrap(~ Species, ncol=4)
)
```

>>>>

<!--

@@

-->

@@

# make plot
suppressWarnings(
	ggplot(aes(x=surrogate.held, y=genetic.held), data=curr.DF) +
		theme_classic() +
		theme(strip.background=element_rect(fill='grey20'), strip.text=element_text(color='white', face='italic', size=2.5)) +
		xlab('Environmental variation secured (%)') +
		ylab('Adaptive genetic variation secured (%)') +
		geom_point(fill='transparent') +
		stat_smooth(method='glm', method.args=list(family='binomial'), fullrange=TRUE,
			se=FALSE, color='blue') +
		geom_text(aes(label=R2_repr), data=curr.DF2, parse=TRUE, hjust=0, size=2.5, color='blue') +
		facet_wrap(~ Species, ncol=4)
)
```

@@

# make plot
suppressWarnings(
	ggplot(aes(x=surrogate.held, y=genetic.held), data=curr.DF) +
		theme_classic() +
		theme(strip.background=element_rect(fill='grey20'), strip.text=element_text(color='white', face='italic', size=5)) +
		xlab('Geographic variation secured (%)') +
		ylab('Neutral genetic variation secured (%)') +
		geom_point(fill='transparent') +
		stat_smooth(method='glm', method.args=list(family='binomial'), fullrange=TRUE,
			se=FALSE, color='blue') +
		geom_text(aes(label=R2_repr), data=curr.DF2, parse=TRUE, hjust=0, size=5, color='blue') +
		facet_wrap(~ Species, ncol=4)
)
```
